### 2022-10-01 Progress_9.tex
Fix capital G for ubuntu
Clean plots

\documentclass[11pt]{report}
% PACKAGES
  \usepackage[a4paper,left=28mm,right=28mm,top=30mm,bottom=30mm]{geometry}
  \usepackage{graphicx,epstopdf}      % Used to import external graphics (figures)
  \usepackage{hyperref}       % Used for referring to links inside and outside the document
  \usepackage[table]{xcolor}  % To include colors 
  \usepackage{amsmath}        % For most of the math symbols and environments (such as \begin{align})
  \usepackage{amssymb}        % For using symbols in the document
  \usepackage{float}          % Arranging of figures on the page
  \usepackage[bf]{caption}    % Arranging the captions in floating environments [bf] makes the Figures bold
  \usepackage{subcaption}     % To arrange captions of subfigures
  \usepackage{booktabs}       % For standard tabular tables, with rules
  \usepackage{tabularx}       % For clean tables such as in the Nomenclature
  \usepackage{fancyhdr}       % Fancy headers
  \usepackage[colorinlistoftodos]{todonotes}      % To create todo notes
  \usepackage[nottoc,notlot,notlof]{tocbibind}    % Add bibliography to content
  \usepackage{bm}             % Make bold symbols
  \usepackage{lipsum}
  \usepackage{parskip}
% LAY-OUT
  % \usepackage{pdfpages}

@@

  \begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth, trim={0.87cm 9.5cm 10cm 1.5cm},clip]{graphics/planning v2.pdf}

@@

  Figure \ref{} shows the reference $u$, together with simulation results of the demonstration. Five signals from this simulation are saved, so that they may be used as a reference for the LfD controllers: $u$, $\dot{u}$, $x^d$, $\dot{x}^d$, and $F_e^d$. Superscript $d$ denotes a result from the demonstration simulation.

  \subsection{Reference spreading}
  To apply reference spreading, the references must be split into an ante- and post-impact reference, and extended. The resulting references are shown in Figure \ref{fig:my_label}. The ante-impact reference is extended after the time of impact, defined as the first timestep where $x>=d$. Furthermore, the post-impact references are extended up to 0.5 seconds after time of impact. This delay prevents extension during an oscillation. Force and velocities were extended with a constant hold, whereas positions were updated to match the new velocity references.

@@

  These controllers were evaluated with the switching references from the previous subsection. Firstly, it will be assumed that the location of the contact surface matches the location during the demonstration, i.e., $w=0$ m. The results are shown in Figure \ref{fig:my_label}.

@@

  In another experiment, the contact surface is moved to $w=0.02$ m when executing the learned reference. This is shown in Figure \ref{fig:my_label}. This experiment gives similar results, in the sense reference spreading results in less peaks compared to during the demonstration, and the impedance controller outperforms the position/force controller.

@@

  % These controllers were evaluated in an ideal scenario, meaning that the impact occurs at the exact same time as it did during the demonstration, and there is a perfect estimation of $F_e^d$. The results are shown in Figure \ref{}.

@@

  \newpage
  \thispagestyle{empty} \ \newpage

>>>>

\documentclass[11pt]{report}
% PACKAGES
  \usepackage[a4paper,left=28mm,right=28mm,top=30mm,bottom=30mm]{geometry}
  \usepackage{graphicx,epstopdf}      % Used to import external graphics (figures)
  \usepackage{hyperref}       % Used for referring to links inside and outside the document
  \usepackage[table]{xcolor}  % To include colors 
  \usepackage{amsmath}        % For most of the math symbols and environments (such as \begin{align})
  \usepackage{amssymb}        % For using symbols in the document
  \usepackage{float}          % Arranging of figures on the page
  \usepackage[bf]{caption}    % Arranging the captions in floating environments [bf] makes the Figures bold
  \usepackage{subcaption}     % To arrange captions of subfigures
  \usepackage{booktabs}       % For standard tabular tables, with rules
  \usepackage{tabularx}       % For clean tables such as in the Nomenclature
  \usepackage{fancyhdr}       % Fancy headers
  \usepackage[colorinlistoftodos]{todonotes}      % To create todo notes
  \usepackage[nottoc,notlot,notlof]{tocbibind}    % Add bibliography to content
  \usepackage{bm}             % Make bold symbols
  \usepackage{lipsum}
  \usepackage{parskip}
  \usepackage[export]{adjustbox}
  \usepackage{changepage}
% LAY-OUT
  % \usepackage{pdfpages}

@@

  \begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth, trim={0.87cm 9.5cm 10cm 1.5cm},clip]{Graphics/planning v2.pdf}

@@

  Figure \ref{fig:1d_demonstration} shows the reference $u$, together with simulation results of the demonstration. Five signals from this simulation are saved, so that they may be used as a reference for the LfD controllers: $u$, $\dot{u}$, $x^d$, $\dot{x}^d$, and $F_e^d$. Superscript $d$ denotes a result from the demonstration simulation.

  \begin{figure}[]
  \centering
  \begin{adjustwidth}{0pt}{5pt}
  \includegraphics[right]{Graphics/1d_demonstration.pdf}
  \end{adjustwidth}
  \caption{Results of the demonstration simulation}
  \label{fig:1d_demonstration}
  \end{figure}

  \begin{figure}[]
  \centering
  \begin{adjustwidth}{0pt}{5pt}
  \includegraphics[right]{Graphics/1d_RS.pdf}
  \end{adjustwidth}
  \caption{Ante- and post-impact references generated from the demonstration data}
  \label{fig:1d_RS}
  \end{figure}

  \subsection{Reference spreading}
  To apply reference spreading, the references must be split into an ante- and post-impact reference, and extended. The resulting references are shown in Figure \ref{fig:1d_RS}. The ante-impact reference is extended after the time of impact, defined as the first timestep where $x\leq d$. Furthermore, the post-impact references are extended up to 0.5 seconds after time of impact. This delay prevents extension during an oscillation. Force and velocities were extended with a constant hold, whereas positions were updated to match the new velocity references.

@@

  These controllers were evaluated with the switching references from the previous subsection. Firstly, it will be assumed that the location of the contact surface matches the location during the demonstration, i.e., $w=0$ m. The results are shown in Figure \ref{fig:1d_learned_w0}.

@@

  In another experiment, the contact surface is moved to $w=0.02$ m when executing the learned reference. This is shown in Figure \ref{fig:1d_learned_w002}. This experiment gives similar results, in the sense reference spreading results in less peaks compared to during the demonstration, and the impedance controller outperforms the position/force controller.

@@

  \begin{figure}[!h]
  \centering
  \begin{adjustwidth}{0pt}{5pt}
  \includegraphics[right]{Graphics/1d_learned_w=0.pdf}
  \end{adjustwidth}
  \caption{Results of both LfD controllers using RS. Impact at $x=0 m.$}
  \label{fig:1d_learned_w0}
  \end{figure}

  \begin{figure}[!h]
  \centering
  \begin{adjustwidth}{0pt}{5pt}
  \includegraphics[right]{Graphics/1d_learned_w=0.02.pdf}
  \end{adjustwidth}
  \caption{Results of both LfD controllers using RS. Impact at $x=0.02 m.$}
  \label{fig:1d_learned_w002}
  \end{figure}
  % These controllers were evaluated in an ideal scenario, meaning that the impact occurs at the exact same time as it did during the demonstration, and there is a perfect estimation of $F_e^d$. The results are shown in Figure \ref{}.

@@

  % \newpage
  % \thispagestyle{empty} \ \newpage
